Glucose ingestion before and after resistance training does not augment ribosome biogenesis in healthy moderately trained young adults

### 2023-04-13 ribose-paper.postfeedback.RMD
misc changes

---
title: "Glucose ingestion before and after resistance training does not augment ribosome biogenesis in healthy moderately trained young adults"
author: "Kristian Lian^1^, Sara<sup>1</sup>, Håvard Hamarsland<sup>1</sup>, Daniel Hammarström<sup>1</sup>, Stian Ellefsen<sup>1</sup>"
bibliography: resources/ribose-paper.bib
csl: resources/jap.csl
output:
  word_document:
    reference_docx: resources/reference-template-02.docx
editor_options: 
  chunk_output_type: console
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = "../output"
    )
  })
---

>>>>

---
title: "Glucose ingestion before and after resistance training does not augment ribosome biogenesis in healthy moderately trained young adults"
author: "Kristian Lian^1^, Sara<sup>1</sup>, Håvard Hamarsland<sup>1</sup>, Daniel Hammarström<sup>1</sup>, Stian Ellefsen<sup>1</sup>"
bibliography: resources/ribose-paper.bib
csl: resources/jap.csl
output:
  word_document:
    reference_docx: resources/reference-template-02.docx
editor_options: 
  chunk_output_type: console
---
